---
title: Descriptive Analyses for SANE Training Program Data
subtitle: | 
          | CSTAT Case: C1788
          | Clients: Rebecca Campbell, Autumn Ashley, & Katherine Dontje
author: 
  - name: Steven J. Pierce
    orcid: 0000-0002-0679-3019
    email: pierces1@msu.edu
    affil-id: 1 
affiliations: 
  - id: 1 
    name: Michigan State University
    department: Center for Statistical Training and Consulting
    url: "[https://cstat.msu.edu](https://cstat.msu.edu)"
bibliography: references.bib          # File holds BibTeX data for references
csl: apa.csl                          # File controls citation & reference list format
params:                               # Default values for parameters
  SourceDir: "scripts/"               # Relative path to folder holding this file
  SourceFile: "Descriptive_Analyses.qmd"    # Name of this script file
  LogFile: "Descriptive_Analyses_Draft.pdf" # Default name of rendered output file
format: 
  pdf:                                # Settings for PDF output
    output-file: "Descriptive_Analyses_Draft.pdf" # Default output file name 
    output-ext: "pdf"                 # Default file name extension
    documentclass: scrartcl           # LaTeX document type
    papersize: letter
    geometry:                         # Control page margins
      - top=1in
      - bottom=1in
      - left=1in
      - right=1in
    number-sections: true           # Auto-number each section
    toc: true                       # Include table of contents (TOC)
    toc-depth: 3                    # Number of layers in TOC
    colorlinks: true
    template-partials: 
      - title.tex   # Controls author affiliation formatting
    include-in-header:
      - file: compact-title.tex    # Controls spacing around title. 
      - text: |
          \usepackage{fancyhdr}
          \usepackage[noblocks]{authblk}
          \renewcommand*{\Authsep}{, }
          \renewcommand*{\Authand}{, }
          \renewcommand*{\Authands}{, }
          \renewcommand\Affilfont{\small}
          \usepackage[yyyymmdd,hhmmss]{datetime}    %% for currenttime command
          \usepackage{lastpage}                     %% For pageref command
          \usepackage{fontspec}
          \defaultfontfeatures{Ligatures=TeX}
          \usepackage[font={small}, margin=1cm, skip=2pt]{caption}
          \usepackage{url}
          \usepackage{floatrow}                     %% For controlling float placement
          \floatsetup[table]{capposition=top}       %% Puts table caption at top.
          \floatsetup[longtable]{margins=centering} %% Centers longtable tables
          \floatplacement{figure}{!ht}              %% Control placement of figures
          \floatplacement{table}{!ht}               %% Control placement of tables
          \usepackage[labelfont=bf, textfont=bf]{caption}  %% For bolded table/figure captions
          \usepackage{placeins}                     %% For FloatBarrier command
          \usepackage{booktabs}                     %% Used by kableExtra
          \usepackage{longtable}                    %% Used by kableExtra
          \usepackage{array}                        %% Used by kableExtra
          \usepackage{multirow}                     %% Used by kableExtra
          \usepackage{wrapfig}                      %% Used by kableExtra
          \usepackage{colortbl}                     %% Used by kableExtra
          \usepackage{pdflscape}                    %% Used by kableExtra
          \usepackage{tabu}                         %% Used by kableExtra
          \usepackage[normalem]{ulem}               %% Used by kableExtra
          \usepackage{makecell}                     %% Used by kableExtra
          \usepackage{xcolor}                       %% Used by kableExtra
          \usepackage{dcolumn}                      %% Used by kableExtra
          \usepackage{threeparttable}               %% Used by kableExtra
          \usepackage{threeparttablex}              %% Used by kableExtra
          \usepackage{amsmath}                      %% for equation support. 
          \usepackage{titling}      
          \usepackage{verbatim}                     %% For comment command
          \pretitle{\begin{center}\LARGE\bfseries\sffamily}
          \posttitle{\end{center}}
          \pagestyle{fancy}
          \lhead{SANETPA Descriptive Analyses}
          \chead{\includegraphics[height=0.85cm]{../graphics/Combomark-Horiz_Pantone-567.eps}}
          \rhead{\today\ \currenttime}
          \cfoot{ }
          \fancyfoot[R]{\thepage\ of \pageref*{LastPage}}
          \renewcommand{\headrulewidth}{0.4pt}
          \renewcommand{\footrulewidth}{0.4pt}
          \fancypagestyle{plain}{\pagestyle{fancy}}
          \newcommand*\tocentryformat[1]{{\sffamily#1}}  %% Fix TOC font style
          \RedeclareSectionCommands                      %% Fix TOC font style
            [
              tocentryformat=\tocentryformat,
              tocpagenumberformat=\tocentryformat
            ]
            {section,subsection,subsubsection,paragraph,subparagraph}
execute:                              # Default Quarto chunk execution options
  eval: true
  echo: fenced                        # Show the code in the output file
  output: true
  warning: true
  error: true
  include: true
knitr:                                # Default R knitr package chunk options
  opts_chunk: 
    message: true
    cfsize: "footnotesize"  
---

\lfoot{\texttt{\small \detokenize{`r params$LogFile`}}}

\FloatBarrier

# Purpose
This file is part of a research compendium [@Pierce-RN8756] associated with a 
study about a sexual assault nurse examiner training program [@Dontje-RN8757]. 
It contains results from descriptive analyses. 

\FloatBarrier

# Setup
This section documents some setup tasks that are useful to the statistician on 
the team. Most readers of this document will probably want skip directly to 
@sec-Read-Data.

\FloatBarrier

## Define Global Options
Global R chunk options are defined in the YAML header but local chunk options
will over-ride global options. We can temporarily disable an individual chunk by
inserting `#| eval: false` on a line at the top of the chunk. The method for
creating a `cfsize` option that controls font size in code chunks and their text
output is based on an answer to a question posted on
[stackoverflow.com](https://stackoverflow.com/a/46526740).

``` {r}
#| label: global-options

# Create a custom chunk hook/option for controlling font size in chunk & output.
def.chunk.hook  <- knitr::knit_hooks$get("chunk")
knitr::knit_hooks$set(chunk = function(x, options) {
  x <- def.chunk.hook(x, options)
  ifelse(options$cfsize != "normalsize", 
         paste0("\n \\", options$cfsize,"\n\n", x, "\n\n \\normalsize"), 
         x)
  })
```

\FloatBarrier

## Load Packages
R packages usually add new functions to the base R software, allowing you to do 
more things. Here, we load the specific R packages required for this script to 
work.

```{r}
#| label: load-packages
library(devtools)       # for session_info()
library(here)           # for here(), i_am(), makes code more portable.
library(rmarkdown)      # for pandoc_version()
library(knitr)          # for kable()
library(dplyr)          # for %>%, filter(), group_by(), mutate(), rename(), etc.
library(tidyverse)      # for map_dfr(), map_chr(), rowid_to_column(), etc.
library(haven)          # for as_factor()
library(labelled)       # for var_label()
options(kableExtra.latex.load_packages = FALSE)
library(kableExtra)     # for kable_styling(), add_header_above(), 
                        # column_spec(), row_spec() etc. 
library(piercer)        # for git_report(), which_latex()
library(PropCIs)        # for scoreci()
library(psych)          # for alpha()
library(quarto)         # for quarto_version()
library(SANETPA)        # for version info 
```

\FloatBarrier

## Declare Path
This next chunk declares the path to this script relative to the project-level 
root directory. If the file is not in the right location under the project root
you'll get a warning message. This helps ensure relative paths are all working 
as expected. The chunk below uses the `SourceDir` and `SourceFile` parameters 
set in the YAML header. 

``` {r}
#| label: declare-path

# Declare path to this script relative to the project root directory.
here::i_am(path = paste0(params$SourceDir, params$SourceFile))
```

\FloatBarrier

# Read Data {#sec-Read-Data}
We start be reading in the datafile, which contains the following datasets:

* `Applicants`. This is a person-level data file containing one row for every 
  applicant, regardless of eligibility status., 
* `Eligible_Applicants`. This is a person-level file containing one row for 
  every person who both applied and was eligible for the program. It omits 
   those who were ineligible. 
* `Thresholds`. This is a person-threshold level file with one row per threshold 
  encountered by each eligible applicant. 

``` {r}
#| label: load-data
#| eval: true

# Store path to data file. 
DataFile <- here("data/Imported_SANETP_Data.RData")

load(file = DataFile)
```

@tbl-imported-data-file shows meta-data about the data file we just loaded and
@tbl-datasets shows the sizes of the datasets it contains. 

```{r}
#| label: tbl-imported-data-file
#| tbl-cap: "Meta-Data About the Data File Loaded"

file.info(DataFile, extra_cols = FALSE) %>% 
  rownames_to_column() %>% 
  mutate(rowname = basename(rowname)) %>% 
  select(-isdir, -mode) %>% 
  kable(, format = "latex", booktabs = TRUE, 
        col.names = c("File Name", "Size (Bytes)", "Modified", 
                      "Last Status Change", "Last Accessed")) %>% 
  kable_styling() %>% 
  column_spec(column = 3:5, width = "2cm")
```


```{r}
#| label: tbl-datasets
#| tbl-cap: "Sizes of the Datasets"

data.frame(Dataset = c("Applicants", "Eligible_Applicants", "Thresholds"),
           N_Rows = c(nrow(Applicants), nrow(Eligible_Applicants), 
                      nrow(Thresholds)),
           N_Cols = c(ncol(Applicants), ncol(Eligible_Applicants), 
                      ncol(Thresholds))) %>% 
  kable(, format = "latex", booktabs = TRUE, 
        col.names = c("Dataset", "N Rows", "N Columns")) %>% 
  kable_styling() 
```

\FloatBarrier

# Summaries of Applicants Data
There are `r nrow(Applicants)` rows in the `Applicants` dataset. The first thing
we need to examine is the distribution for a few key variables.
@tbl-Stage-Raw-Eligible shows the crosstabulation of the raw stage variable by
the eligibility status.

```{r}
#| label: tbl-Stage-Raw-Eligible
#| tbl-cap: Stage_Raw by Eligible Contingency Table

# Footnote text. 
FN <- "CSW, clinical skills workshop; DT, didactic training."

xtabs(~as_factor(Stage_Raw) + Eligible, addNA = TRUE, 
      data = Applicants) %>% 
  addmargins() %>% 
  kable(format = "latex", booktabs = TRUE, 
        col.names = c("Stage_Raw", "No", "Yes", "Sum")) %>% 
  kable_styling() %>% 
  add_header_above(header = c(" ", "Eligible" = 2, " ")) %>% 
  column_spec(column = 4, italic = TRUE) %>% 
  row_spec(row = 8, italic = TRUE) %>% 
  footnote(kable_input = ., general = FN, footnote_as_chunk = TRUE, 
           threeparttable = TRUE)
```

:::{.callout-tip}
* People who exited at the Applied stage should all be coded as ineligible. 
* People in the remaining stages should all be coded as eligible. 
* Cell count for Applied/Yes should be 0. Positive values there may be a result 
  of inaccurate data entry (we previously detected and fixed 4 cases with this 
  check). 

:::

The next thing to examine is the eligibility rate (see @tbl-Eligible-Rate). 

```{r}
#| label: tbl-Eligible-Rate
#| tbl-cap: Eligibility Rate Among All Applicants

FN <- paste("We used a Wilson score interval for the 95% confidence interval.")

ER <- mean(Applicants$Eligible)
ERCI <- scoreci(x = sum(Applicants$Eligible), n = nrow(Applicants), 
                conf.level = 0.95)

data.frame(No = sum(1 - Applicants$Eligible),
           Yes = sum(Applicants$Eligible),
           Total = nrow(Applicants),
           Rate = mean(Applicants$Eligible),
           LL = ERCI$conf.int[1],
           UL = ERCI$conf.int[2]) %>% 
  kable(format = "latex", booktabs = TRUE, digits = c(0, 0, 0, 2, 2, 2), 
        format.args = list(nsmall = c(0, 0, 0, 2, 2, 2))) %>% 
  kable_styling() %>% 
  add_header_above(header = c("Eligible (N)" = 3, " ", "95% CI" = 2)) %>% 
  footnote(kable_input = ., general = FN, footnote_as_chunk = TRUE, 
           threeparttable = TRUE)
```

@tbl-Time-Demands-Eligible shows the joint distribution of the `Barrier_TD` 
scale score and the `Eligible` indicator. This allows us to demonstrate that 
all eligible applicants have observed scale scores in the expected range and all 
ineligible applicants have missing values. 

```{r}
#| label: tbl-Time-Demands-Eligible
#| tbl-cap: Barrier_TD by Eligible Contingency Table

# Footnote text. 
FN <- paste("The range of possible values for Barrier_TD is [3, 15].",
            "NA, not available (missing data).")

xtabs(~Barrier_TD + Eligible, addNA = TRUE, data = Applicants) %>% 
  addmargins() %>% 
  kable(format = "latex", booktabs = TRUE, 
        col.names = c("Barrier_TD", "No", "Yes", "Sum")) %>% 
  kable_styling() %>% 
  add_header_above(header = c(" ", "Eligible" = 2, " ")) %>% 
  column_spec(column = 4, italic = TRUE) %>% 
  row_spec(row = 8, italic = TRUE) %>% 
  footnote(kable_input = ., general = FN, footnote_as_chunk = TRUE, 
           threeparttable = TRUE)
```

\FloatBarrier

# Summaries of Eligible Applicants Data
There are `r nrow(Eligible_Applicants)` rows in the `Eligible_Applicants` 
dataset. 

\FloatBarrier

## Outcome Distribution
@tbl-Stage-Reached shows the frequency distribution for the stage reached among 
the eligible applicants. This is the stage variable we will use for modeling. 

```{r}
#| label: tbl-Stage-Reached
#| tbl-cap: Stage_Reached Frequency Distribution Among Eligible Applicants

# Footnote text. 
FN <- paste("Denominator for percents is total number of eligible applicants.", 
      "CSW, clinical skills workshop; DT, didactic training.")

xtabs(~as_factor(Stage_Reached), addNA = TRUE, 
      data = Eligible_Applicants) %>% 
  addmargins() %>% 
  as.data.frame() %>% 
  rename(Stage_Reached = as_factor.Stage_Reached.) %>% 
  mutate(Percent = 100*Freq/nrow(Eligible_Applicants),
         Cumulative = if_else(Stage_Reached == "Sum", 
                              true = 100, 
                              false = cumsum(Percent))) %>% 
  kable(format = "latex", booktabs = TRUE, digits = 1,
        col.names = c("Stage_Reached", "Freq", "%", "Cumulative %")) %>% 
  kable_styling() %>% 
  row_spec(row = 6, italic = TRUE) %>% 
  footnote(kable_input = ., general = FN, footnote_as_chunk = TRUE, 
           threeparttable = TRUE)
```

@tbl-Setting-original shows the frequency distribution for the setting where 
eligible applicants practice in its original coding. It shows that the Tribal 
category is too small to model as a separate level,, so we need to combine it 
with another category. 

```{r}
#| label: tbl-Setting-original
#| tbl-cap: Original Practice Setting Frequency Distribution Among Eligible Applicants

# Footnote text. 
FN <- paste("Denominator for percents is total number of eligible applicants.")

xtabs(~as_factor(practicset_dem_num), addNA = TRUE, 
      data = Eligible_Applicants) %>% 
  addmargins() %>% 
  as.data.frame() %>% 
  rename(practicset_dem_num = as_factor.practicset_dem_num.) %>% 
  mutate(Percent = 100*Freq/nrow(Eligible_Applicants),
         Cumulative = if_else(practicset_dem_num == "Sum", 
                              true = 100, 
                              false = cumsum(Percent))) %>% 
  kable(format = "latex", booktabs = TRUE, digits = 1,
        col.names = c("practicset_dem_num", "Freq", "%", "Cumulative %")) %>% 
  kable_styling() %>% 
  row_spec(row = 5, italic = TRUE) %>% 
  footnote(kable_input = ., general = FN, footnote_as_chunk = TRUE, 
           threeparttable = TRUE)
```

@tbl-Setting-recoded shows the updated frequency distribution it after 
collapsing the Rural and Tribal categories together. This glosses over important 
cultural differences between those settings, but these are the two settings most 
similar in size. 
 
```{r}
#| label: tbl-Setting-recoded
#| tbl-cap: Recoded Practice Setting Frequency Distribution Among Eligible Applicants

# Footnote text. 
FN <- paste("Denominator for percents is total number of eligible applicants.")

xtabs(~as_factor(Setting), addNA = TRUE, data = Eligible_Applicants) %>% 
  addmargins() %>% 
  as.data.frame() %>% 
  rename(Setting = as_factor.Setting.) %>% 
  mutate(Percent = 100*Freq/nrow(Eligible_Applicants),
         Cumulative = if_else(Setting == "Sum", 
                              true = 100, 
                              false = cumsum(Percent))) %>% 
  kable(format = "latex", booktabs = TRUE, digits = 1,
        col.names = c("Setting (Recoded)", "Freq", "%", "Cumulative %")) %>% 
  kable_styling() %>% 
  row_spec(row = 4, italic = TRUE) %>% 
  footnote(kable_input = ., general = FN, footnote_as_chunk = TRUE, 
           threeparttable = TRUE)
```

# Summaries of Thresholds Data
@fig-Stages shows the final set of stages and thresholds between them at which
attrition from the training program could occur. The arrows associated with each
threshold are labeled according to how the outcome variable is coded on the
corresponding person-threshold record, depending on whether the person
stopped participating at the current stage or moved on to the next stage.

```{dot}
//| label: fig-Stages
//| fig-cap: Stages, Thresholds (T1-T4), and Stopping Ratios (SR1-SR4) in the 
//|          SANE Training Program. CSW, clinical skills workshop; DT, didactic 
//|          training.
//| fig-width: 6
//| fig-height: 3

digraph StagesModeled {

graph [rankdir="LR"];

node [shape = "box", style= "filled", fillcolor = "Gray90", fontsize = "7"];
A1 [label = "Attrited 1\nNot Enrolled\nSR1"]
A2 [label = "Attrited 2\nBefore DT\nSR2"]
A3 [label = "Attrited 3\nDuring DT\nSR3"]
A4 [label = "Attrited 4\nBefore CSW\nSR4"]

S1 [label = "Stage 1\nEligible"]
S2 [label = "Stage 2\nEnrolled"]
S3 [label = "Stage 3\nStarted DT"]
S4 [label = "Stage 4\nFinished DT"]
S5 [label = "Stage 5\nFinished CSW"]

edge [fontsize = "7"];

S1 -> A1 [label = "T1\nAttrit = 1"]
S2 -> A2 [label = "T2\nAttrit = 1"]
S3 -> A3 [label = "T3\nAttrit = 1"]
S4 -> A4 [label = "T4\nAttrit = 1"]

S1 -> S2 [label = "Attrit = 0"]
S2 -> S3 [label = "Attrit = 0"]
S3 -> S4 [label = "Attrit = 0"]
S4 -> S5 [label = "Attrit = 0"]
}
```

```{r}
#| label: tbl-Threshold-Attrit
#| tbl-cap: Threshold by Attrit Contingency Table

# Footnote text. 
FN <- paste("Denominator for percents is row N.", 
            "CSW, clinical skills workshop; DT, didactic training; N, number",
            "of participants who reached the from stage.")

Thresholds %>% 
  mutate(Threshold = as_factor(Threshold),
         Attrit = as_factor(Attrit)) %>% 
  group_by(Threshold, Attrit) %>% 
  summarise(N = n()) %>% 
  pivot_wider(names_from = Attrit, values_from = N) %>% 
  mutate(N = No + Yes,
         Percent = 100*Yes/N) %>% 
  select(Threshold, N, No, Yes, Percent) %>% 
  kable(format = "latex", booktabs = TRUE, digits = 1, 
        col.names= c("Threshold (from/to)", "N", "No (0)", 
                     "Yes (1)", "%")) %>% 
  kable_styling() %>% 
  add_header_above(header = c(" " = 2, "Attrit" = 3)) %>% 
  footnote(kable_input = ., general = FN, footnote_as_chunk = TRUE, 
           threeparttable = TRUE)
```

# References
::: {#refs}
:::

\FloatBarrier

# Software Information
This section documents information that is important for reproducibility. Most
users will not need to read it. It is primarily here for use by the statistician 
on the team if we need to troubleshoot reproducibility issues because someone 
else is unable to get the same results from the same code. Start by checking for 
differences in package versions. 

We used [R](https://www.r-project.org/) as our main computing environment and
[Quarto](https://quarto.org/) scripts to enhance reproducibility. We used
[RStudio](www.rstudio.org) as the editor to interface with R and Quarto.

- Software chain:
  **qmd file > RStudio > Quarto > R > knitr > md file > Pandoc > tex file > TinyTeX > PDF file**.
- Source file: \texttt{\detokenize{`r params$SourceFile`}} 
- Output file: \texttt{\detokenize{`r params$LogFile`}} 
- [Quarto `r quarto_version()`](https://quarto.org/) runs `*.qmd` files through 
  [R](https://www.r-project.org/) and [knitr](https://yihui.org/knitr/) to 
  produce `*.md` markdown files.
- [Pandoc `r rmarkdown::pandoc_version()`](https://pandoc.org) converts markdown 
  files (`*.md`) to other formats, including LaTeX (`*.tex`) and HTML (`*.html`) 
  among others.
- [TinyTeX](https://yihui.org/tinytex/) compiles LaTeX files (`*.tex`) into PDF 
  files. It should be viable to use [MiKTeX](https://miktex.org) or another 
  LaTeX distribution instead. 

\FloatBarrier

## Versions
This document was generated using the following computational environment and 
dependencies:

```{r}
#| label: show-version
#| echo: true

# Check and report whether we used TinyTex or other LaTeX software. 
which_latex()

# Get R and R package version numbers in use.
devtools::session_info()
```

\FloatBarrier

## Git Details
The current Git commit details and status are:

``` {r}
#| label: git-details
#| echo: true

git_report()
```

This is useful because it tells us exactly which commit in the Git history 
we would need to be using to make sure we are running the exact same code. 
Sometimes another person is not using the most current code, or has changed the 
code in some way since it was last committed.  

::: {.callout-tip}
* Untracked files are files located in the repository that Git has not been told 
  to entirely ignore, but have also not been committed into the version history. 
* Unstaged changes to files indicate that some of the contents have been 
  modified since the last time the file was committed to Git. In production 
  runs, we want the Git output to not show any unstaged changes to key files!

::: 
