---
title: Export Diagram for SANE Training Program Data
subtitle: | 
          | CSTAT Case: C1788
          | Clients: Rebecca Campbell, Autumn Ashley, & Katherine Dontje
author: 
  - name: Steven J. Pierce
    orcid: 0000-0002-0679-3019
    email: pierces1@msu.edu
    affil-id: 1 
affiliations: 
  - id: 1 
    name: Michigan State University
    department: Center for Statistical Training and Consulting
    url: "[https://cstat.msu.edu](https://cstat.msu.edu)"
bibliography: references.bib          # File holds BibTeX data for references
csl: apa.csl                          # File controls citation & reference list format
params:                               # Default values for parameters
  SourceDir: "scripts/"               # Relative path to folder holding this file
  SourceFile: "Export_Diagram.qmd"    # Name of this script file
  LogFile: "Export_Diagram_Draft.pdf" # Default name of rendered output file
format: 
  pdf:                                # Settings for PDF output
    output-file: "Export_Diagram_Draft.pdf" # Default output file name 
    output-ext: "pdf"                 # Default file name extension
    documentclass: scrartcl           # LaTeX document type
    papersize: letter
    geometry:                         # Control page margins
      - top=1in
      - bottom=1in
      - left=1in
      - right=1in
    number-sections: true           # Auto-number each section
    toc: true                       # Include table of contents (TOC)
    toc-depth: 3                    # Number of layers in TOC
    colorlinks: true
    template-partials: 
      - title.tex   # Controls author affiliation formatting
    include-in-header:
      - file: compact-title.tex    # Controls spacing around title. 
      - text: |
          \usepackage{fancyhdr}
          \usepackage[noblocks]{authblk}
          \renewcommand*{\Authsep}{, }
          \renewcommand*{\Authand}{, }
          \renewcommand*{\Authands}{, }
          \renewcommand\Affilfont{\small}
          \usepackage[yyyymmdd,hhmmss]{datetime}    %% for currenttime command
          \usepackage{lastpage}                     %% For pageref command
          \usepackage{fontspec}
          \defaultfontfeatures{Ligatures=TeX}
          \usepackage[font={small}, margin=1cm, skip=2pt]{caption}
          \usepackage{url}
          \usepackage{floatrow}                     %% For controlling float placement
          \floatsetup[table]{capposition=top}       %% Puts table caption at top.
          \floatsetup[longtable]{margins=centering} %% Centers longtable tables
          \floatplacement{figure}{!ht}              %% Control placement of figures
          \floatplacement{table}{!ht}               %% Control placement of tables
          \usepackage[labelfont=bf, textfont=bf]{caption}  %% For bolded table/figure captions
          \usepackage{placeins}                     %% For FloatBarrier command
          \usepackage{booktabs}                     %% Used by kableExtra
          \usepackage{longtable}                    %% Used by kableExtra
          \usepackage{array}                        %% Used by kableExtra
          \usepackage{multirow}                     %% Used by kableExtra
          \usepackage{wrapfig}                      %% Used by kableExtra
          \usepackage{colortbl}                     %% Used by kableExtra
          \usepackage{pdflscape}                    %% Used by kableExtra
          \usepackage{tabu}                         %% Used by kableExtra
          \usepackage[normalem]{ulem}               %% Used by kableExtra
          \usepackage{makecell}                     %% Used by kableExtra
          \usepackage{xcolor}                       %% Used by kableExtra
          \usepackage{dcolumn}                      %% Used by kableExtra
          \usepackage{threeparttable}               %% Used by kableExtra
          \usepackage{threeparttablex}              %% Used by kableExtra
          \usepackage{amsmath}                      %% for equation support. 
          \usepackage{titling}      
          \usepackage{verbatim}                     %% For comment command
          \pretitle{\begin{center}\LARGE\bfseries\sffamily}
          \posttitle{\end{center}}
          \pagestyle{fancy}
          \lhead{SANETPA Export Diagram}
          \chead{\includegraphics[height=0.85cm]{../graphics/Combomark-Horiz_Pantone-567.pdf}}
          \rhead{\today\ \currenttime}
          \cfoot{ }
          \fancyfoot[R]{\thepage\ of \pageref*{LastPage}}
          \renewcommand{\headrulewidth}{0.4pt}
          \renewcommand{\footrulewidth}{0.4pt}
          \fancypagestyle{plain}{\pagestyle{fancy}}
          \newcommand*\tocentryformat[1]{{\sffamily#1}}  %% Fix TOC font style
          \RedeclareSectionCommands                      %% Fix TOC font style
            [
              tocentryformat=\tocentryformat,
              tocpagenumberformat=\tocentryformat
            ]
            {section,subsection,subsubsection,paragraph,subparagraph}
execute:                              # Default Quarto chunk execution options
  eval: true
  echo: fenced                        # Show the code in the output file
  output: true
  warning: true
  error: true
  include: true
knitr:                                # Default R knitr package chunk options
  opts_chunk: 
    message: true
    cfsize: "tiny"  
---

\lfoot{\texttt{\small \detokenize{`r params$LogFile`}}}

\FloatBarrier

# Purpose
This file is part of a research compendium [@Pierce-RN8756] associated with a 
study about a sexual assault nurse examiner training program [@Dontje-RN8757]. 
It just exports a diagram we want to include in a manuscript to a graphics file. 

\FloatBarrier

# Setup
This section documents some setup tasks that are useful to the statistician on 
the team. Most readers of this document will probably want skip directly to 
@sec-Read-Data.

\FloatBarrier

## Define Global Options
Global R chunk options are defined in the YAML header but local chunk options
will over-ride global options. We can temporarily disable an individual chunk by
inserting `#| eval: false` on a line at the top of the chunk. The method for
creating a `cfsize` option that controls font size in code chunks and their text
output is based on an answer to a question posted on
[stackoverflow.com](https://stackoverflow.com/a/46526740).

``` {r}
#| label: global-options

# Create a custom chunk hook/option for controlling font size in chunk & output.
def.chunk.hook  <- knitr::knit_hooks$get("chunk")
knitr::knit_hooks$set(chunk = function(x, options) {
  x <- def.chunk.hook(x, options)
  ifelse(options$cfsize != "normalsize", 
         paste0("\n \\", options$cfsize,"\n\n", x, "\n\n \\normalsize"), 
         x)
  })
```

\FloatBarrier

## Load Packages
R packages usually add new functions to the base R software, allowing you to do 
more things. Here, we load the specific R packages required for this script to 
work.

```{r}
#| label: load-packages
library(devtools)       # for session_info()
library(here)           # for here(), i_am(), makes code more portable.
library(rmarkdown)      # for pandoc_version()
library(knitr)          # for kable()
library(DiagrammeR)     # for create_edge_df(), create_graph(), 
                        #     create_node_df(), export_graph()
library(magick)         # for image_read(), image_write()
library(piercer)        # for file_details(), git_report(), which_latex()
library(quarto)         # for quarto_version()
library(SANETPA)        # for version info 
```

\FloatBarrier

## Declare Path
This next chunk declares the path to this script relative to the project-level 
root directory. If the file is not in the right location under the project root
you'll get a warning message. This helps ensure relative paths are all working 
as expected. The chunk below uses the `SourceDir` and `SourceFile` parameters 
set in the YAML header. 

``` {r}
#| label: declare-path

# Declare path to this script relative to the project root directory.
here::i_am(path = paste0(params$SourceDir, params$SourceFile))
```

\FloatBarrier

# Stage Diagram
@fig-Stages shows the final set of stages and thresholds between them at which
attrition from the training program could occur. The arrows associated with each
threshold are labeled according to how the outcome variable is coded on the
corresponding person-threshold record, depending on whether the person
stopped participating at the current stage or moved on to the next stage.

```{dot}
//| label: fig-Stages
//| fig-cap: Stages, Thresholds (T1-T3), and Stopping Ratios (SR1-SR3) in the 
//|          SANE Training Program. CSW, clinical skills workshop; DT, didactic 
//|          training.
//| fig-width: 5
//| fig-height: 2.5

digraph StagesModeled {

graph [rankdir="LR"];

node [shape = "box", style= "filled", fillcolor = "Gray90", fontsize = "7"];
A1 [label = "Attrited\nBefore DT\nSR1"]
A2 [label = "Attrited\nDuring DT\nSR2"]
A3 [label = "Attrited\nBefore/During CSW\nSR3"]

S1 [label = "Stage 1\nEnrolled"]
S2 [label = "Stage 2\nStarted DT"]
S3 [label = "Stage 3\nFinished DT"]
S4 [label = "Stage 4\nFinished CSW"]

edge [fontsize = "7", arrowsize = 0.5];

S1 -> A1 [label = "T1\nAttrit = 1"]
S2 -> A2 [label = "T2\nAttrit = 1"]
S3 -> A3 [label = "T3\nAttrit = 1"]

S1 -> S2 [label = "Attrit = 0"]
S2 -> S3 [label = "Attrit = 0"]
S3 -> S4 [label = "Attrit = 0"]

}
```

Below, I use the `DiagrammeR` package to create a graph object corresponding to 
the contents of @fig-Stages. 

```{r}
#| label: create-diagram

my_nodes <- create_node_df(n = 7, shape = "box", style= "filled", 
                           color = "black", fillcolor = "Gray90", 
                           fontname = "Times New Roman", fontsize = "12",
                           fontcolor = "black", fixedsize = FALSE, 
                           label = c("Attrited\nBefore DT\nSR1", 
                                     "Attrited\nDuring DT\nSR2",
                                     "Attrited\nBefore/During CSW\nSR3",
                                     "Stage 1\nEnrolled",
                                     "Stage 2\nStarted DT",
                                     "Stage 3\nFinished DT",
                                     "Stage 4\nFinished CSW"))

my_edges <- create_edge_df(from = c(4, 5, 6, 4, 5, 6),
                           to =   c(1, 2, 3, 5, 6, 7),
                           label = c("T1\nAttrit = 1",
                                     "T2\nAttrit = 1",
                                     "T3\nAttrit = 1",
                                     "Attrit = 0",
                                     "Attrit = 0",
                                     "Attrit = 0"),
                           fontname = "Times New Roman", fontsize = "12",
                           color = "black", arrowsize = 0.5)

stage_diagram <- create_graph(nodes_df = my_nodes, edges_df = my_edges,
                              directed = TRUE, attr_theme = "lr",
                              graph_name = "StagesModeled")
```

Now we need to export the graph to a PNG file with sufficient resolution. I 
converted the `fig-width` and `fig-height` settings for @fig-Stages from inches 
to pixels in `export_graph()` width and height settings by multiplying by 300 
dpi. 

```{r}
#| label: export-diagram-png

png_file <- paste0("scripts/output/Campbell_Figure_1_", Sys.Date(), ".png")

export_graph(graph = stage_diagram, 
             file_name = here(png_file),
             file_type = "png", width = 1500, height = 750)

file_details(here(png_file))
```

Now, I read in the PNG file and convert it to a TIFF file suitable for 
submission to the intended journal (which requires a JPEG or TIFF file with 
dpi $\ge$ 300). 

```{r}
#| label: convert-diagram-tif

tif_file <- paste0("scripts/output/Campbell_Figure_1_", Sys.Date(), ".tif")

image_write(image = image_read(path = here(png_file)), 
            path = here(tif_file), 
            format = "tiff")

file_details(here(tif_file))
```

\FloatBarrier

# References
::: {#refs}
:::

\FloatBarrier

# Software Information
This section documents information that is important for reproducibility. Most
users will not need to read it. It is primarily here for use by the statistician 
on the team if we need to troubleshoot reproducibility issues because someone 
else is unable to get the same results from the same code. Start by checking for 
differences in package versions. 

We used [R](https://www.r-project.org/) as our main computing environment and
[Quarto](https://quarto.org/) scripts to enhance reproducibility. We used
[RStudio](www.rstudio.org) as the editor to interface with R and Quarto.

- Software chain:
  **qmd file > RStudio > Quarto > R > knitr > md file > Pandoc > tex file > TinyTeX > PDF file**.
- Source file: \texttt{\detokenize{`r params$SourceFile`}} 
- Output file: \texttt{\detokenize{`r params$LogFile`}} 
- [Quarto `r quarto_version()`](https://quarto.org/) runs `*.qmd` files through 
  [R](https://www.r-project.org/) and [knitr](https://yihui.org/knitr/) to 
  produce `*.md` markdown files.
- [Pandoc `r rmarkdown::pandoc_version()`](https://pandoc.org) converts markdown 
  files (`*.md`) to other formats, including LaTeX (`*.tex`) and HTML (`*.html`) 
  among others.
- [TinyTeX](https://yihui.org/tinytex/) compiles LaTeX files (`*.tex`) into PDF 
  files. It should be viable to use [MiKTeX](https://miktex.org) or another 
  LaTeX distribution instead. 

\FloatBarrier

## Versions
This document was generated using the following computational environment and 
dependencies:

```{r}
#| label: show-version
#| echo: true

# Check and report whether we used TinyTex or other LaTeX software. 
which_latex()

# Get R and R package version numbers in use.
devtools::session_info()
```

\FloatBarrier

## Git Details
The current Git commit details and status are:

``` {r}
#| label: git-details
#| echo: true

git_report()
```

This is useful because it tells us exactly which commit in the Git history 
we would need to be using to make sure we are running the exact same code. 
Sometimes another person is not using the most current code, or has changed the 
code in some way since it was last committed.  

::: {.callout-tip}
* Untracked files are files located in the repository that Git has not been told 
  to entirely ignore, but have also not been committed into the version history. 
* Unstaged changes to files indicate that some of the contents have been 
  modified since the last time the file was committed to Git. In production 
  runs, we want the Git output to not show any unstaged changes to key files!

::: 
