---
title: Import and Manage SANE Training Program Data
subtitle: | 
          | CSTAT Case: C1788
          | Clients: Campbell, Rebecca; Ashley, Autumn; Dontje, Katherine
author: 
  - name: Steven J. Pierce
    orcid: 0000-0002-0679-3019
    email: pierces1@msu.edu
    affiliations: 
      - name: Michigan State University, Center for Statistical Training and Consulting  ([https://cstat.msu.edu](https://cstat.msu.edu))
bibliography: references.bib          # File holds BibTeX data for references
csl: apa.csl                          # File controls citation & reference list format
params:                               # Default values for parameters
  SourceDir: "scripts/"               # Relative path to folder holding this file
  SourceFile: "Import_Data.qmd"       # Name of this script file
  LogFile: "Import_Data_Draft.html"   # Default name of rendered output file
date: now                             # Sets Date Published = when script is rendered
date-modified: last-modified          # Sets Date Modified = when code was last saved
date-format: YYYY-MM-DD HH:mm:ss z    # Show date, time, & timezone
css: CSTAT_style.css                  # File formats title banner block w/ logo.
title-block-banner: true              # Enable the banner, per CSTAT_style.css 
title-block-banner-color: "#18453B"   # Spartan Green color for title text. 
format: 
  html:                               # Settings for HTML output
    output-file: "Import_Data_Draft.html"      # Default output file name
    theme: [default, brand, CSTAT_theme.scss]  # Theme controls output formatting
    toc: true                         # Include table of contents (TOC)
    toc-depth: 3                      # Number of layers in TOC
    toc-location: left                # Where to display the TOC
    number-sections: true             # Auto-number each section
    number-depth: 3                   # Number of layers for section numbering
    code-fold: true                   # Default to collapsing code chunks
    code-tools: true                  # Adds control for show/hide all code
    code-line-numbers: false          # Skip numbering lines in code chunks
    embed-resources: true             # Makes HTML output file self-contained
    anchor-sections: true             # Allow linking to section headings
execute:                              # Default Quarto chunk execution options
  eval: true
  echo: fenced                        # Show the code in the output file
  output: true
  warning: true
  error: true
  include: true
knitr:                                # Default R knitr package chunk options
  opts_chunk: 
    message: true
---

\FloatBarrier

# Purpose
This file is part of a research compendium [@Pierce-RN8756] associated with a 
study about a sexual assault nurse examiner training program [@Dontje-RN8757]. 
It imports data from from an SPSS data file provided by the investigators, does
some data cleaning and management, then saves out an R data file that will be 
used by the analyses scripts in this compendium. 

# Setup
This section documents some setup tasks that are useful to the statistician on 
the team. Most readers of this document will probably want skip directly to 
@sec-Data-Mgt.

## Define Global Options
Global R chunk options are defined in the YAML header but local chunk options
will over-ride global options. We can temporarily disable an individual chunk by
inserting `#| eval: false` on a line at the top of the chunk.

## Load Packages
R packages usually add new functions to the base R software, allowing you to do 
more things. Here, we load the specific R packages required for this script to 
work.

```{r}
#| label: load-packages
library(here)           # for here(), i_am(), makes code more portable.
library(devtools)       # for session_info()
library(rmarkdown)      # for pandoc_version()
library(knitr)          # for kable()
library(dplyr)          # for %>%, filter(), group_by(), mutate(), rename(), etc.
library(haven)          # for read_SPSS()
options(kableExtra.latex.load_packages = FALSE)
library(kableExtra)     # for kable_styling(), add_header_above(), 
                        # column_spec(), row_spec() etc. 
library(kableExtra)     # for kable_styling 
library(piercer)        # for git_report(), sim_2arm_prepost()
library(quarto)         # for quarto_version()
library(SANETPA)        # for version info 
```

## Declare Path
This next chunk declares the path to this script relative to the project-level 
root directory. If the file is not in the right location under the project root
you'll get a warning message. This helps ensure relative paths are all working 
as expected. The chunk below uses the `SourceDir` and `SourceFile` parameters 
set in the YAML header. 

``` {r}
#| label: declare-path

# Declare path to this script relative to the project root directory.
here::i_am(path = paste0(params$SourceDir, params$SourceFile))
```

# Data Management {#sec-Data-Mgt}

## Read Data {#sec-Read-Data}
The raw data provided by the investigators is in an SPSS data file. This section 
imports it into an R data frame/tibble. The raw data is de-identified to 
preserve participant privacy and protect confidentiality.

```{r}
#| label: import-data
#| eval: false

SANETP_RAW <- read_spss(here("scripts/extdata/Filename.sav")) 
names(SANETP_RAW)
```

# Save Data

``` {r}
#| label: create-save-what

# Character vector of object names that will be saved.
save_what <- c("SANETP_RAW")
```

``` {r}
#| label: save-data
#| eval: false

save(list = save_what, 
     file=here("data/Imported_SANETP_Data.RData"))
```

::: {.callout-tip}
The current data file can be loaded into R by copying the following code chunk 
into a script, setting the chunk option `eval: true`, and running the chunk. 
That will overwrite any objects already in memory that have the same names as 
the objects being loaded.

``` {r}
#| label: load-data
#| eval: false

load(file=here("data/Imported_SANETP_Data.RData"))
```
:::

# References
::: {#refs}
:::

# Software Information
This section documents information that is important for reproducibility. Most
users will not need to read it. It is primarily here for use by the statistician 
on the team if we need to troubleshoot reproducibility issues because someone 
else is unable to get the same results from the same code. Start by checking for 
differences in package versions. 

We used [R](https://www.r-project.org/) as our main computing environment and
[Quarto](https://quarto.org/) scripts to enhance reproducibility. We used
[RStudio](www.rstudio.org) as the editor to interface with R and Quarto.

- Software chain:
  **qmd file > RStudio > Quarto > R > knitr > md file > Pandoc > HTML file**.
- Source file: **`{r} paste0(params$SourceDir, params$SourceFile)`**
- Output file: **`{r} paste0(params$SourceDir, "output/", params$LogFile)`**
- [Quarto `{r} quarto_version()`](https://quarto.org/) runs `*.qmd` files through 
  [R](https://www.r-project.org/) and [knitr](https://yihui.org/knitr/) to 
  produce `*.md` markdown files.
- [Pandoc `{r} rmarkdown::pandoc_version()`](https://pandoc.org) converts 
  markdown files (`*.md`) to other formats, including LaTeX (`*.tex`) and HTML 
  (`*.html`) among others.

## Versions
This document was generated using the following computational environment and 
dependencies:

```{r}
#| label: show-version
#| echo: true

# Get R and R package version numbers in use.
devtools::session_info()
```

## Git Details
The current Git commit details and status are:

``` {r}
#| label: git-details
#| echo: true

git_report()
```

This is useful because it tells us exactly which commit in the Git history 
we would need to be using to make sure we are running the exact same code. 
Sometimes another person is not using the most current code, or has changed the 
code in some way since it was last committed.  

::: {.callout-tip}
Untracked files are files located in the repository that Git has not been told 
to entirely ignore, but have also not been commited into the version history. 

Unstaged changes to files indicate that some of the contents have been modified 
since the last time the file was committed to Git. In production runs, we want 
the Git output to not show any unstaged changes to key files!
::: 
