---
title: Research Question 4 Analyses for SANE Training Program Data
subtitle: | 
          | CSTAT Case: C1788
          | Clients: Rebecca Campbell, Autumn Ashley, & Katherine Dontje
author: 
  - name: Steven J. Pierce
    orcid: 0000-0002-0679-3019
    email: pierces1@msu.edu
    affil-id: 1 
affiliations: 
  - id: 1 
    name: Michigan State University
    department: Center for Statistical Training and Consulting
    url: "[https://cstat.msu.edu](https://cstat.msu.edu)"
bibliography: references.bib          # File holds BibTeX data for references
csl: apa.csl                          # File controls citation & reference list format
params:                               # Default values for parameters
  SourceDir: "scripts/"               # Relative path to folder holding this file
  SourceFile: "RQ4_Analyses.qmd"    # Name of this script file
  LogFile: "RQ4_Analyses_Draft.pdf" # Default name of rendered output file
format: 
  pdf:                                # Settings for PDF output
    output-file: "RQ4_Analyses_Draft.pdf" # Default output file name 
    output-ext: "pdf"                 # Default file name extension
    documentclass: scrartcl           # LaTeX document type
    papersize: letter
    geometry:                         # Control page margins
      - top=1in
      - bottom=1in
      - left=1in
      - right=1in
    number-sections: true           # Auto-number each section
    toc: true                       # Include table of contents (TOC)
    toc-depth: 3                    # Number of layers in TOC
    colorlinks: true
    template-partials: 
      - title.tex   # Controls author affiliation formatting
    include-in-header:
      - file: compact-title.tex    # Controls spacing around title. 
      - text: |
          \usepackage{fancyhdr}
          \usepackage[noblocks]{authblk}
          \renewcommand*{\Authsep}{, }
          \renewcommand*{\Authand}{, }
          \renewcommand*{\Authands}{, }
          \renewcommand\Affilfont{\small}
          \usepackage[yyyymmdd,hhmmss]{datetime}    %% for currenttime command
          \usepackage{lastpage}                     %% For pageref command
          \usepackage{fontspec}
          \defaultfontfeatures{Ligatures=TeX}
          \usepackage[font={small}, margin=1cm, skip=2pt]{caption}
          \usepackage{url}
          \usepackage{floatrow}                     %% For controlling float placement
          \floatsetup[table]{capposition=top}       %% Puts table caption at top.
          \floatsetup[longtable]{margins=centering} %% Centers longtable tables
          \floatplacement{figure}{!ht}              %% Control placement of figures
          \floatplacement{table}{!ht}               %% Control placement of tables
          \usepackage[labelfont=bf, textfont=bf]{caption}  %% For bolded table/figure captions
          \usepackage{placeins}                     %% For FloatBarrier command
          \usepackage{booktabs}                     %% Used by kableExtra
          \usepackage{longtable}                    %% Used by kableExtra
          \usepackage{array}                        %% Used by kableExtra
          \usepackage{multirow}                     %% Used by kableExtra
          \usepackage{wrapfig}                      %% Used by kableExtra
          \usepackage{colortbl}                     %% Used by kableExtra
          \usepackage{pdflscape}                    %% Used by kableExtra
          \usepackage{tabu}                         %% Used by kableExtra
          \usepackage[normalem]{ulem}               %% Used by kableExtra
          \usepackage{makecell}                     %% Used by kableExtra
          \usepackage{xcolor}                       %% Used by kableExtra
          \usepackage{dcolumn}                      %% Used by kableExtra
          \usepackage{threeparttable}               %% Used by kableExtra
          \usepackage{threeparttablex}              %% Used by kableExtra
          \usepackage{amsmath}                      %% for equation support. 
          \usepackage{titling}      
          \usepackage{verbatim}                     %% For comment command
          \pretitle{\begin{center}\LARGE\bfseries\sffamily}
          \posttitle{\end{center}}
          \pagestyle{fancy}
          \lhead{SANETPA RQ4 Analyses}
          \chead{\includegraphics[height=0.85cm]{../graphics/Combomark-Horiz_Pantone-567.pdf}}
          \rhead{\today\ \currenttime}
          \cfoot{ }
          \fancyfoot[R]{\thepage\ of \pageref*{LastPage}}
          \renewcommand{\headrulewidth}{0.4pt}
          \renewcommand{\footrulewidth}{0.4pt}
          \fancypagestyle{plain}{\pagestyle{fancy}}
          \newcommand*\tocentryformat[1]{{\sffamily#1}}  %% Fix TOC font style
          \RedeclareSectionCommands                      %% Fix TOC font style
            [
              tocentryformat=\tocentryformat,
              tocpagenumberformat=\tocentryformat
            ]
            {section,subsection,subsubsection,paragraph,subparagraph}
execute:                              # Default Quarto chunk execution options
  eval: true
  echo: fenced                        # Show the code in the output file
  output: true
  warning: true
  error: true
  include: true
knitr:                                # Default R knitr package chunk options
  opts_chunk: 
    message: true
    cfsize: "tiny"  
---

\lfoot{\texttt{\small \detokenize{`r params$LogFile`}}}

\FloatBarrier

# Purpose
This file is part of a research compendium [@Pierce-RN8756] associated with a 
study about a sexual assault nurse examiner training program [@Dontje-RN8757]. 
The training program had two major components: didactic training (DT) followed 
by a clinical skills workshop (CSW). This file contains results from analyses 
that address RQ4.

# Research Question

* **RQ4.** For the participants who completed DT and those who completed the 
  CSW, to what extent did they find each training component to be 
  useful/helpful?

\FloatBarrier

# Setup
This section documents some setup tasks that are useful to the statistician on 
the team. Most readers of this document will probably want skip directly to 
@sec-Read-Data.

\FloatBarrier

## Define Global Options
Global R chunk options are defined in the YAML header but local chunk options
will over-ride global options. We can temporarily disable an individual chunk by
inserting `#| eval: false` on a line at the top of the chunk. The method for
creating a `cfsize` option that controls font size in code chunks and their text
output is based on an answer to a question posted on
[stackoverflow.com](https://stackoverflow.com/a/46526740).

``` {r}
#| label: global-options

# Create a custom chunk hook/option for controlling font size in chunk & output.
def.chunk.hook  <- knitr::knit_hooks$get("chunk")
knitr::knit_hooks$set(chunk = function(x, options) {
  x <- def.chunk.hook(x, options)
  ifelse(options$cfsize != "normalsize", 
         paste0("\n \\", options$cfsize,"\n\n", x, "\n\n \\normalsize"), 
         x)
  })
```

\FloatBarrier

## Load Packages
R packages usually add new functions to the base R software, allowing you to do 
more things. Here, we load the specific R packages required for this script to 
work.

```{r}
#| label: load-packages
library(devtools)       # for session_info()
library(here)           # for here(), i_am(), makes code more portable.
library(rmarkdown)      # for pandoc_version()
library(knitr)          # for kable()
library(dplyr)          # for %>%, filter(), group_by(), mutate(), rename(), etc.
library(broom)          # for broom()
library(effectsize)     # for hedges_g()
library(tidyverse)      # for map(), map_dfr(), map_chr(), rowid_to_column(), 
                        # unnest(), etc.
library(haven)          # for as_factor()
library(janitor)        # for adorn_totals()
library(labelled)       # for get_variable_labels()
options(kableExtra.latex.load_packages = FALSE)
library(kableExtra)     # for kable_styling(), add_header_above(), 
                        # column_spec(), row_spec() etc. 
library(piercer)        # for dc_summary(), file_details(), git_report(), 
                        # which_latex()
library(psych)          # for alpha()
library(quarto)         # for quarto_version()
library(SANETPA)        # for version info 
```

\FloatBarrier

## Declare Path
This next chunk declares the path to this script relative to the project-level 
root directory. If the file is not in the right location under the project root
you'll get a warning message. This helps ensure relative paths are all working 
as expected. The chunk below uses the `SourceDir` and `SourceFile` parameters 
set in the YAML header. 

``` {r}
#| label: declare-path

# Declare path to this script relative to the project root directory.
here::i_am(path = paste0(params$SourceDir, params$SourceFile))
```

\FloatBarrier

## Read Data {#sec-Read-Data}
We start by reading in the datafile, which contains the following datasets that 
we need for RQ1 analyses:

* `Applicants`. This is a person-level data file containing one row for every 
  applicant, regardless of eligibility status., 
* `Eligible_Applicants`. This is a person-level file containing one row for 
  every person who both applied and was eligible for the program. It omits 
   those who were ineligible. 

``` {r}
#| label: load-data
#| eval: true

# Store path to data file. 
DataFile <- here("data/Imported_SANETP_Data.RData")

load(file = DataFile)
```

@tbl-imported-data-file shows meta-data about the data file we just loaded. 

```{r}
#| label: tbl-imported-data-file
#| tbl-cap: "Meta-Data About the Data File Loaded"

file_details(DataFile) %>% 
  kable(, format = "latex", booktabs = TRUE, 
        col.names = c("File Name", "Size", "Last Modified")) %>% 
  kable_styling() 
```

## Create Subsets of Data {#sec-Update-Data}
For RQ4, we derive two additional subsets of the `Enrolled_Applicants` data. We 
create the new scale score variables measuring training satisfaction
(`DT_Satisfaction` and `CSW_Satisfaction`) while creating those datasets.

First, we need the subset of `Enrolled_Applicants` that completed the DT
component because we need to examine their satisfaction with the first part 
of the training program. The chunk below creates the `Completed_DT` dataset

```{r}
#| label: create-Completed-DT

Completed_DT <- Enrolled_Applicants %>% 
  filter(Stage_Reached >= 3) %>% 
  rowwise() %>%
  mutate(DT_Satisfaction = mean(c_across(Didactic_Sat_1:Didactic_Sat_7), 
                               na.rm = TRUE)) %>%
  ungroup() 
```

Second, we need the subset of `Enrolled_Applicants` that completed the CSW 
training component so we can examine their satisfaction with that second part of 
the training program. The chunk below creates the `Completed_CSW`.

```{r}
#| label: create-Completed-CSW

Completed_CSW <- Enrolled_Applicants %>% 
  filter(Stage_Reached == 4)  %>% 
  rowwise() %>%
  mutate(CSW_Satisfaction = mean(c_across(CSW_Sat_1:CSW_Sat_7), 
                                na.rm = TRUE)) %>%
  ungroup() 
```

@tbl-datasets shows the shows the sizes of the datasets used in RQ4 analyses. 

```{r}
#| label: tbl-datasets
#| tbl-cap: "Sizes of the Datasets Used for RQ1"

data.frame(Dataset = c("Enrolled_Applicants", "Completed_DT", "Completed_CSW"),
           N_Rows = c(nrow(Enrolled_Applicants), nrow(Completed_DT), 
                      nrow(Completed_CSW)),
           N_Cols = c(ncol(Enrolled_Applicants), ncol(Completed_DT), 
                      ncol(Completed_CSW))) %>% 
  kable(., format = "latex", booktabs = TRUE, 
        col.names = c("Dataset", "N Rows", "N Columns")) %>% 
  kable_styling() 
```

\FloatBarrier

# Methods {#sec-Methods}
This section describes the data sources, measures, and statistical methods used 
to answer RQ1. 

\FloatBarrier

## Data Sources
We rely on two different datasets for answering RQ4. The `Completed_DT` dataset 
has one row per enrolled applicant who completed the DT component of the program 
($N = `r nrow(Completed_DT)`$). Meanwhile, the `Completed_CSW` dataset contains 
one row per enrolled applicant who completed the CSW component of the program 
($N = `r nrow(Completed_CSW)`$). 

## Measures {#sec-Measures}
The sections below describe the measures used to answer RQ4. 

\FloatBarrier

### DT Satisfaction
Satisfaction with the DT component of the program was measured by the set of 7
items shown in @tbl-DT-Satisfaction-items. The response options comprised a
5-point Likert scale with values from 1 (*strongly disagree*) to 5 (*strongly
agree*). All items were worded such that higher values indicated greater
satisfaction. An overall scale score was obtained by taking the unweighted mean 
of the non-missing items. 

```{r}
#| label: tbl-DT-Satisfaction-items
#| tbl-cap: DT Satisfaction Items

# Table footnote
FN <- paste("The response options were on a 5-point Likert scale: 1 (strongly",
            "disagree), 2 (somewhat disagree), 3 (neither agree nor disagree)", 
            "4 (somewhat agree), 5 (strongly agree).")

DT_Items <- Completed_DT %>% 
  select(starts_with("Didactic_Sat_")) %>% 
  get_variable_labels() %>% 
  as_tibble() %>% 
  pivot_longer(cols = everything(), names_to = "Variable", 
               values_to = "Label") %>% 
  mutate(Label = str_replace_all(string = Label, pattern = ":I", 
                                 replacement = ": I"))

DT_Items %>% 
  kable(format = "latex", booktabs = TRUE) %>% 
  kable_styling(font_size = 9) %>% 
  column_spec(column = 2, width = "10cm") %>% 
  footnote(kable_input = ., general = FN, footnote_as_chunk = TRUE,
           threeparttable = TRUE)
```

\FloatBarrier

### CSW Satisfaction
Satisfaction with the CSW component of the program was measured by the set of 7
items shown in @tbl-CSW-Satisfaction-items. The response options comprised a
5-point Likert scale with values from 1 (*strongly disagree*) to 5 (*strongly
agree*). All items were worded such that higher values indicated greater
satisfaction. An overall scale score was obtained by taking the unweighted mean 
of the non-missing items. 

```{r}
#| label: tbl-CSW-Satisfaction-items
#| tbl-cap: CSW Satisfaction Items

CSW_Items <- Completed_CSW %>% 
  select(starts_with("CSW_Sat_")) %>% 
  get_variable_labels() %>% 
  as_tibble() %>% 
  pivot_longer(cols = everything(), names_to = "Variable", 
               values_to = "Label") %>% 
  mutate(Label = str_replace_all(string = Label, pattern = "_x000D_", 
                                 replacement = " "))

CSW_Items %>% 
  kable(format = "latex", booktabs = TRUE) %>% 
  kable_styling(font_size = 9) %>% 
  column_spec(column = 2, width = "10cm") %>% 
  footnote(kable_input = ., general = FN, footnote_as_chunk = TRUE,
           threeparttable = TRUE)
```

\FloatBarrier

## Statistical Analyses 
For each of the two satisfaction scales, we first examine item-level frequency
distributions, then used the psych package for R [@Revelle-RN2324] to estimate
Cronbach's alpha as a measure of reliability for the unweighted scale scores, 
and then provide descriptive statistics and graphs of the scale score
distributions.

# Results 

\FloatBarrier

## DT Satisfaction

\FloatBarrier

### Item Distributions

```{r}
#| label: tbl-DT-Satisfaction-freqs
#| tbl-cap: Frequency Distributions for DT Satisfaction Items

# Table footnote
FN <- paste("The response options were on a 5-point Likert scale: 1 (strongly",
            "disagree), 2 (somewhat disagree), 3 (neither agree nor disagree)", 
            "4 (somewhat agree), 5 (strongly agree).")

Completed_DT %>% 
  select(starts_with("Didactic_Sat_")) %>% 
  pivot_longer(cols = everything(), names_to = "Variable", 
               values_to = "Value") %>% 
  mutate(Value = addNA(factor(Value, levels = 1:5))) %>% 
  group_by(Variable, .drop = FALSE) %>% 
  count(Value) %>% 
  mutate(pct = 100*n/nrow(Completed_DT)) %>% 
  ungroup() %>% 
  left_join(., DT_Items, by = join_by(Variable)) %>%  
  relocate(Variable, Label) %>% 
  kable(format = "latex", booktabs = TRUE, digits = 1, 
        col.names = c("Item", "Label", "Value", "n", "%")) %>% 
  kable_styling(font_size = 9) %>% 
  column_spec(column = 2, width = "10cm") %>% 
  collapse_rows(columns = 1:2, valign = "top", latex_hline = "major",
                row_group_label_position = "first", headers_to_remove = 0) %>% 
  footnote(kable_input = ., general = FN, footnote_as_chunk = TRUE,
           threeparttable = TRUE)
```

\FloatBarrier

### Scale Score Reliability

```{r}
#| label: reliability-Barrier-TD-3item

Completed_DT %>% 
  select(Didactic_Sat_1, Didactic_Sat_2, Didactic_Sat_3, Didactic_Sat_4,
         Didactic_Sat_5, Didactic_Sat_6, Didactic_Sat_7) %>% 
  as.data.frame() %>% 
  alpha(x = ., cumulative = TRUE, discrete = TRUE)
```

\FloatBarrier

### Scale Score Distribution

```{r}
#| label: tbl-DT-Satisfaction
#| tbl-cap: Descriptive Statistics for DT Satisfaction Among Enrolled Applicants 
#|          Who Completed the DT Component 

# Footnote text.
FN <- paste("N_m, number of missing values; N_o, number of observed values.")

VNames <- c("DT_Satisfaction", "Didactic_Sat_1", "Didactic_Sat_2", 
            "Didactic_Sat_3", "Didactic_Sat_4", "Didactic_Sat_5", 
            "Didactic_Sat_6", "Didactic_Sat_7")
CNames <- c("Variable", "N", "N_m", "N_o", "Mean", "SD", "Min", "Max")

Completed_DT %>% 
  select(ID, DT_Satisfaction, Didactic_Sat_1, Didactic_Sat_2, Didactic_Sat_3, 
         Didactic_Sat_4, Didactic_Sat_5, Didactic_Sat_6, Didactic_Sat_7) %>% 
  pivot_longer(cols = c(DT_Satisfaction, Didactic_Sat_1, Didactic_Sat_2, 
                        Didactic_Sat_3, Didactic_Sat_4, Didactic_Sat_5, 
                        Didactic_Sat_6, Didactic_Sat_7),
               names_to = "VarName", 
               values_to = "Value") %>% 
  mutate(VarName = factor(VarName, levels = VNames, labels = VNames)) %>% 
  relocate(ID, VarName) %>% 
  group_by(VarName) %>% 
  summarise(N = n(),
            N_missing = sum(is.na(Value)), 
            N_observed = sum(!is.na(Value)), 
            Mean = mean(Value, na.rm = TRUE),
            SD = sd(Value, na.rm = TRUE),
            Min = round(min(Value, na.rm = TRUE), digits = 1),
            Max = max(Value, na.rm = TRUE)) %>% 
  kable(., format = "latex", booktabs = TRUE, digits = 1, 
        col.names = CNames, row.names = FALSE) %>% 
  kable_styling() %>% 
  footnote(kable_input = ., general = FN, footnote_as_chunk = TRUE)
```

```{r}
#| label: fig-DT-Satisfaction
#| fig-cap: Histogram of DT Satisfaction Among Enrolled Applicants 
#|          Who Completed the DT Component 
#| fig-width: 5
#| fig-height: 2.5
#| warning: false

ggplot(data = Completed_DT, aes(x = DT_Satisfaction)) +
  geom_histogram(aes(y = after_stat(density)), binwidth = 0.1, color = "black", 
                 fill = "grey") +
  geom_density(alpha = .6, fill = "#FF6666") +
  geom_vline(aes(xintercept = mean(DT_Satisfaction, na.rm = TRUE)), color = "blue", 
             linetype = "solid", linewidth = 1) +
  coord_cartesian(xlim = c(1, 5), ylim = c(0, 4)) + 
  scale_x_continuous(breaks = seq(from = 1, to = 5, by = 1)) +
  scale_y_continuous(breaks = seq(from = 0, to = 4, by = 0.5)) +
  theme_bw() +
  labs(x = "DT Satisfaction", 
       y = "Density")
```

\FloatBarrier

## CSW Satisfaction

\FloatBarrier

### Item Distributions

```{r}
#| label: tbl-CSW-Satisfaction-freqs
#| tbl-cap: Frequency Distributions for CSW Satisfaction Items

# Table footnote
FN <- paste("The response options were on a 5-point Likert scale: 1 (strongly",
            "disagree), 2 (somewhat disagree), 3 (neither agree nor disagree)", 
            "4 (somewhat agree), 5 (strongly agree).")

Completed_CSW %>% 
  select(starts_with("CSW_Sat_")) %>% 
  pivot_longer(cols = everything(), names_to = "Variable", 
               values_to = "Value") %>% 
  mutate(Value = addNA(factor(Value, levels = 1:5))) %>% 
  group_by(Variable, .drop = FALSE) %>% 
  count(Value) %>% 
  mutate(pct = 100*n/nrow(Completed_CSW)) %>% 
  ungroup() %>% 
  left_join(., CSW_Items, by = join_by(Variable)) %>%  
  relocate(Variable, Label) %>% 
  kable(format = "latex", booktabs = TRUE, digits = 1, 
        col.names = c("Item", "Label", "Value", "n", "%")) %>% 
  kable_styling(font_size = 9) %>% 
  column_spec(column = 2, width = "10cm") %>% 
  collapse_rows(columns = 1:2, valign = "top", latex_hline = "major",
                row_group_label_position = "first", headers_to_remove = 0) %>% 
  footnote(kable_input = ., general = FN, footnote_as_chunk = TRUE,
           threeparttable = TRUE)
```

\FloatBarrier

### Scale Score Reliability

```{r}
#| label: reliability-CSW-Satisfaction

Completed_CSW %>% 
  select(CSW_Sat_1, CSW_Sat_2, CSW_Sat_3, CSW_Sat_4, CSW_Sat_5, CSW_Sat_6, 
  CSW_Sat_7) %>% 
  as.data.frame() %>% 
  alpha(x = ., cumulative = TRUE, discrete = TRUE)
```

\FloatBarrier

### Scale Score Distribution

```{r}
#| label: tbl-CSW-Satisfaction
#| tbl-cap: Descriptive Statistics for CSW Satisfaction Among Enrolled Applicants 
#|          Who Completed the CSW Component 

# Footnote text.
FN <- paste("N_m, number of missing values; N_o, number of observed values.")

VNames <- c("CSW_Satisfaction", "CSW_Sat_1", "CSW_Sat_2", "CSW_Sat_3", 
            "CSW_Sat_4", "CSW_Sat_5", "CSW_Sat_6", "CSW_Sat_7")
CNames <- c("Variable", "N", "N_m", "N_o", "Mean", "SD", "Min", "Max")

Completed_CSW %>% 
  select(ID, CSW_Satisfaction, CSW_Sat_1, CSW_Sat_2, CSW_Sat_3, CSW_Sat_4, 
        CSW_Sat_5, CSW_Sat_6, CSW_Sat_7) %>% 
  pivot_longer(cols = c(CSW_Satisfaction, CSW_Sat_1, CSW_Sat_2, CSW_Sat_3, 
                        CSW_Sat_4, CSW_Sat_5, CSW_Sat_6, CSW_Sat_7),
               names_to = "VarName", 
               values_to = "Value") %>% 
  mutate(VarName = factor(VarName, levels = VNames, labels = VNames)) %>% 
  relocate(ID, VarName) %>% 
  group_by(VarName) %>% 
  summarise(N = n(),
            N_missing = sum(is.na(Value)), 
            N_observed = sum(!is.na(Value)), 
            Mean = mean(Value, na.rm = TRUE),
            SD = sd(Value, na.rm = TRUE),
            Min = round(min(Value, na.rm = TRUE), digits = 1),
            Max = max(Value, na.rm = TRUE)) %>% 
  kable(., format = "latex", booktabs = TRUE, digits = 1, 
        col.names = CNames, row.names = FALSE) %>% 
  kable_styling() %>% 
  footnote(kable_input = ., general = FN, footnote_as_chunk = TRUE)
```

```{r}
#| label: fig-CSW-Satisfaction
#| fig-cap: Histogram of CSW Satisfaction Among Enrolled Applicants 
#|          Who Completed the CSW Component 
#| fig-width: 5
#| fig-height: 2.5
#| warning: false

ggplot(data = Completed_CSW, aes(x = CSW_Satisfaction)) +
  geom_histogram(aes(y = after_stat(density)), binwidth = 0.1, color = "black", 
                 fill = "grey") +
  geom_density(alpha = .6, fill = "#FF6666") +
  geom_vline(aes(xintercept = mean(CSW_Satisfaction, na.rm = TRUE)), color = "blue", 
             linetype = "solid", linewidth = 1) +
  coord_cartesian(xlim = c(1, 5), ylim = c(0, 8)) + 
  scale_x_continuous(breaks = seq(from = 1, to = 5, by = 1)) +
  scale_y_continuous(breaks = seq(from = 0, to = 8, by = 0.5)) +
  theme_bw() +
  labs(x = "CSW Satisfaction", 
       y = "Density")
```

\FloatBarrier

# Conclusions {#sec-Conclusions}
Both the DT and CSW satisfaction scale scores have sufficient reliability
Cronbach's alpha of 0.75 and 0.78, respectively. All the items for each scale
have reasonable face validity, are moderately and positively correlated with
other items, and contribute to improved reliability of the measure.

The item-level frequency distributions show strongly skewed distributions, with 
responses concentrated in the somewhat agree and strongly agree values, such 
that item means are nearly all > 4.7. 

Consequently, the scale scores for both DT and CSW satisfaction are also 
very skewed and concentrated in the upper end of the possible range. Applicants 
who completed each of these training components were highly satisfied with the 
training they received. 

# References
::: {#refs}
:::

\FloatBarrier

# Software Information
This section documents information that is important for reproducibility. Most
users will not need to read it. It is primarily here for use by the statistician 
on the team if we need to troubleshoot reproducibility issues because someone 
else is unable to get the same results from the same code. Start by checking for 
differences in package versions. 

We used [R](https://www.r-project.org/) as our main computing environment and
[Quarto](https://quarto.org/) scripts to enhance reproducibility. We used
[RStudio](www.rstudio.org) as the editor to interface with R and Quarto.

- Software chain:
  **qmd file > RStudio > Quarto > R > knitr > md file > Pandoc > tex file > TinyTeX > PDF file**.
- Source file: \texttt{\detokenize{`r params$SourceFile`}} 
- Output file: \texttt{\detokenize{`r params$LogFile`}} 
- [Quarto `r quarto_version()`](https://quarto.org/) runs `*.qmd` files through 
  [R](https://www.r-project.org/) and [knitr](https://yihui.org/knitr/) to 
  produce `*.md` markdown files.
- [Pandoc `r rmarkdown::pandoc_version()`](https://pandoc.org) converts markdown 
  files (`*.md`) to other formats, including LaTeX (`*.tex`) and HTML (`*.html`) 
  among others.
- [TinyTeX](https://yihui.org/tinytex/) compiles LaTeX files (`*.tex`) into PDF 
  files. It should be viable to use [MiKTeX](https://miktex.org) or another 
  LaTeX distribution instead. 

\FloatBarrier

## Versions
This document was generated using the following computational environment and 
dependencies:

```{r}
#| label: show-version
#| echo: true

# Check and report whether we used TinyTex or other LaTeX software. 
which_latex()

# Get R and R package version numbers in use.
devtools::session_info()
```

\FloatBarrier

## Git Details
The current Git commit details and status are:

``` {r}
#| label: git-details
#| echo: true

git_report()
```

This is useful because it tells us exactly which commit in the Git history 
we would need to be using to make sure we are running the exact same code. 
Sometimes another person is not using the most current code, or has changed the 
code in some way since it was last committed.  

::: {.callout-tip}
* Untracked files are files located in the repository that Git has not been told 
  to entirely ignore, but have also not been committed into the version history. 
* Unstaged changes to files indicate that some of the contents have been 
  modified since the last time the file was committed to Git. In production 
  runs, we want the Git output to not show any unstaged changes to key files!

::: 
